\cvsection{Open-source Projects}

\subnote{I develop web projects in my free time. Code is available on \href{https://github.com/jennydaman}{Github}.}

\begin{cventries}
  \project{Mind Matter}{jennydaman/mindmatter}
  {
    \begin{cvitems}
      \item{An educational Chrome extension. \href{https://chrome.google.com/webstore/detail/mind-matter/ailffedpjgpjbdadlieaccchpcdiafjc}{Description and prototype available from the Chrome Web Store}.}
      \item{Front-end JavaScript technologies include Preact and Webpack.}
    \end{cvitems}
  }
  \project{Let's Talk!}{twlinux/lets-talk}
  {
    \begin{cvitems}
      \item{Intentionally vulnerable website for beginners to learn about basic code injection vulnerabilities.}
      \item{Front-end designed with \href{http://materializecss.com/}{materialize-css} and \href{https://jquery.com/}{jQuery}.}
      \item{\href{https://expressjs.com/}{Express} and \href{https://www.mysql.com/}{MySQL} back-end supported by \href{Docker} containers and \href{https://docs.docker.com/compose/overview/}{docker-compose}.}
      \item{Shared to reddit, more than 200 upvotes on \href{https://www.reddit.com/r/HowToHack/comments/7zcfqd/i_made_an_easytohack_web_application_for/?ref=share&ref_source=link}{/r/HowToHack} and 9 stars on Github.}
    \end{cvitems}
  }
  \project{TWLinux}{twlinux/twlinux.github.io}
  {
    \begin{cvitems}
      \item{Collection of concise guides about concepts regarding Linux and cyber-security.}
      \item{Hosted on Github pages, based on the jekyll theme \href{https://github.com/daattali/beautiful-jekyll}{daattali/beautiful-jekyll}.}
      \item{Contributed several pull requests to upstream repository, related to CSS bugfixes, CSS customization, and use of Docker.}
    \end{cvitems}
  }

\end{cventries}